---
title: "Algerian Housing Project"
output: html_notebook
---

```{r include=FALSE}
#requir packages
library(dplyr)
library(readr)
library(stringr)
library(ggplot2)
library(ggthemes)
library(cowplot)
library(ggmap)
library(leaflet)
library(htmltools)
library(scales)
library(corrplot)

```

#Import the housing_data

```{r include=FALSE}

housing_data <- read_csv("Housing_Data.csv")
```
 
#View the raw data
 
```{r} 
head(housing_data)
```


```{r}
dim(housing_data)
```
# subseting an variable of interest

```{r}
housing_data2<- housing_data %>% 
  select( Nb.Etage, Nb.Piece,Superficie, Prix.value.dzd,Garage, 
         Jardin,Meuble,Promotion, Paiement, commune, Quartier,Top_Commune,
         date,hour, month, year,Announcer_Type, Announcer_Name,
         Nombre.de.vues, lon, lat) %>% 
        arrange(desc(Prix.value.dzd),Superficie)
```

```{r}
dim(housing_data2)
```
```{r}
head(housing_data2)
```


#create tow variables "cat_vae", "num_var" to distinguiche catégoriales from numerics variables

#1.Numeric variables 
```{r}
num_var <- names(housing_data2)[which(sapply(housing_data2, is.numeric))]
num_var
```
#2.Catégorial variables
```{r}
cat_var <- names(housing_data2)[which(sapply(housing_data2, is.character))]
cat_var
```

#The structure of the data
```{r}
summary(housing_data2[num_var])
```

we see a illogical value in "Nb.Etage", maybe a missentred values

```{r}
housing_data2 %>% group_by(Nb.Etage) %>% count()
```


we them s outliers and turn them ton NA's

```{r} 
housing_data2 <- housing_data2 %>% mutate(Nb.Etage=ifelse(Nb.Etage >15, NA, Nb.Etage))
```
```{r}
summary(housing_data2$Nb.Etage)
```
```{r}
ggplot(housing_data2, aes(Nb.Etage))+ geom_histogram()+
  scale_x_continuous(breaks = seq(1,15))
```


# Catégorial variables
```{r}
summary(housing_data2[cat_var])
```

#convert somme character variables to factors

```{r}
housing_data2 <-  housing_data2 %>% mutate_if(is.character, as.factor)
```


```{r}
summary(housing_data2[cat_var])
```

# check the Duplicates

```{r}
sum(duplicated(housing_data2))
```

# view the duplicates rouws.

```{r}
housing_data2 %>% filter(duplicated(housing_data2) ==TRUE)
```

#Delete the duplicates.

```{r}
housing_data2 <- housing_data2 %>% filter(duplicated(housing_data2)==FALSE)
 dim(housing_data2)
```

#Dealing wiyh missing values and outliers.

what columns in the housing_data2 data frame contain missing values?

```{r}
colSums(sapply(housing_data2, is.na))
```


 Note : (Garage, Jardin , Meuble,  Promotion, Paiement) have the same number of NA's (506), 
 and the same for Announcer_Type and Announcer_Name  (513 NA's).


#1.chek if the are in same rouws Garage, jardin, meuble, promtion, paiment:  

```{r}
housing_data2  %>% filter(is.na(Garage))
```

#2. chek for Announcer_Type and Announcer_Name:

```{r}
housing_data2 %>% select(Prix.value.dzd,Announcer_Type, Announcer_Name, Garage) %>% filter(is.na(Announcer_Type))
```

Note :  there are many startigies to deal with NA's , the simple is to delete theme, in order to not reduce the number of obsevation here we tairte theme  case per case

# we do some exploration to our predictors varables

# wich house's catégorie is the most commun  ?

```{r}
commun_nb_piece<- housing_data2 %>% count(Nb.Piece, sort=TRUE) %>% mutate(Percentage= percent(n /sum(n)) )
commun_nb_piece
```
we see the house with 3 rooms are the most commun in Algiers  (the half )

```{r}
 ggplot(commun_nb_piece, aes(Nb.Piece,n ))+geom_bar(stat="identity", fill="#BBBB99")+
  theme_gdocs()+
  scale_x_continuous(breaks=seq(1,7))

```
# how many houses have a grage, jardin a meuble ?
   and ho many are promotion ?

```{r}
p1 <-  housing_data2 %>%filter(complete.cases(Meuble)) %>%
ggplot(housing_data2, mapping = aes(Nb.Piece, fill=Meuble ))+
geom_bar()+ scale_fill_manual(values = c("#77b7b2","#999999")) 


p2 <- housing_data2 %>%filter(complete.cases(Garage)) %>%
ggplot(housing_data2, mapping = aes(Nb.Piece, fill=Garage ))+
geom_bar()+ scale_fill_manual(values = c("#77b7b2","#999999")) 

p3 <- housing_data2 %>%filter(complete.cases(Jardin)) %>%
ggplot(housing_data2, mapping = aes(Nb.Piece, fill=Jardin))+
geom_bar()+ scale_fill_manual(values = c("#77b7b2","#999999")) 

p4 <-  housing_data2 %>%filter(complete.cases(Promotion)) %>%
ggplot(housing_data2, mapping = aes(Nb.Piece, fill= Promotion))+
geom_bar()+ scale_fill_manual(values = c("#77b7b2","#999999")) 
plot_grid(p1, p2, p3 ,p4,labels = c("House with Meuble", "House with Garage", "House with Jardin", "House with Promotion"), ncol= 2)

  
```

# Number houses in each year 

```{r}
nbr_house_year <- housing_data2 %>% count(year, sort=TRUE)
nbr_house_year
```
#Tomake the analysis more efficient we drop the tow years with less Obs

```{r}
housing_data2<- housing_data2 %>% filter(year!=2012& year!=2013)
```

```{r}
ggplot(nbr_house_year ,aes(year,n) )+
geom_bar(stat="identity", fill="#7fcdbb")+
  labs(title="Number of house / year")
```

#Number of houses per month

```{r}
nbr_house_month <-  housing_data2 %>% count(month, sort=TRUE)
nbr_house_month
```


```{r}
ggplot(nbr_house_month, aes(x= reorder(month,n), n))+
  geom_bar(stat = "identity", fill="#66c2a4")+
  ggtitle(" Numbre of houses / month")+
  xlab("month")+
  ylab("number of house")+
    coord_flip()
   
```
we know aour stady finsh in feb 2017
```{r}
housing_data2 %>% filter(year !=2017) %>% 
 count(month) %>% 
ggplot(aes(x= reorder(month,n), n))+geom_bar(stat = "identity", fill="#66c2a4")+
  ggtitle(" Numbre of houses / month")+
  xlab("month")+
  ylab("number of house")+
    coord_flip()
```


#Number houses between 2016/2017  per commune

```{r}
housing_data2 %>% filter(year==c(2016, 2017)) %>% 
  group_by(year, Top_Commune) %>%
  summarise(count=n())%>% # nbr annoce partop_commune 2016/2017
  
ggplot(aes(x= reorder(Top_Commune, count), count))+geom_bar(stat = "identity", fill="#880011")+
  geom_text(aes(label = count),  hjust =1.1, color= "white")+
  ggtitle(" Numbre of add  Top_Commune 2016 / 2017")+
  xlab("Top_Commun")+
    coord_flip()+
    facet_wrap(~as.factor(year))
```

We focus on our taget variable 
#Price's Distibution.
```{r}
summary(housing_data2$Prix.value.dzd)
```

```{r}
ggplot(housing_data2, aes(x=Prix.value.dzd ))+  geom_histogram(col = 'white', fill="#880011") + 
  theme_light()+scale_x_continuous(labels = comma)+
ggtitle("Distribution of  house prices in Algiers ")

```


#Distribution des prix , Garage , jardin

```{r}
housing_data2 %>% filter(complete.cases(Garage)) %>% 
ggplot( aes(x = Jardin, y=Prix.value.dzd, color= Garage))+
geom_boxplot()+
theme_light()+scale_y_continuous(labels = comma)
```
#Distribution of parices with/no Promotion or Paiement

```{r}
housing_data2 %>% filter(complete.cases(Promotion)) %>% 
ggplot( aes(x = Promotion, y=Prix.value.dzd, color= Paiement))+
geom_boxplot()+
theme_light()+scale_y_continuous(labels = comma)
```
 Note : we romve the outliers
 
#Distribution de Superficier
```{r}
housing_data2 <- housing_data2 %>% filter(Prix.value.dzd < 50000000)
```
```{r}
summary(housing_data2$Prix.value.dzd)
```
```{r}
housing_data2 %>%  
ggplot( aes(x=Superficie ))+geom_histogram(fill="#770000", col="white")+
ggtitle("Distribution de Superficier (m2) ")

```

#Distribution de Superficie , Garage , jardin

```{r}
housing_data2 %>% filter(complete.cases(Garage)) %>% 
ggplot( aes(x = Jardin, y=Superficie, color= Garage))+
geom_boxplot()+
theme_light()+
scale_y_continuous(labels = comma)
```
 we romove the outliers
 
#par superficie
```{r}
housing_data2 <- housing_data2 %>% filter(Superficie <400)

ggplot(housing_data2,aes(x=Superficie, y=Prix.value.dzd ))+
geom_point()+
geom_smooth()+
theme_light()+
scale_y_continuous(labels = comma)
```


# Distribution of price per years

```{r}
ggplot(housing_data2,aes(x= Prix.value.dzd, fill= as.factor(year)))+
  geom_density(col=NA, alpha=0.4 )+
  theme_light()+
  scale_x_continuous(labels = comma)+
   theme(axis.text.y=element_blank())
```
# Price distribution per month

```{r}
ggplot(housing_data2, aes(as.factor(month), Prix.value.dzd))+geom_boxplot(aes(fill=as.factor(month)))+#dist Prix par mois
   theme_light()+scale_y_continuous(labels = comma)+
  theme(legend.position="none") +
  xlab("months")+
  ylab("Price")
 
```

#Time line
```{r}
 month_year <-  housing_data2 %>% group_by(month, year) %>% summarise(nbr=n()) %>% arrange(desc(nbr))
 month_year
```

```{r}
 month_year$month <- match(month_year$month,month.abb)
```

#plot time line

```{r}
ggplot(month_year) + 
  geom_line(aes(month,nbr,group=as.factor(year),color=as.factor(year))) + 
  theme_gdocs() + 
  scale_color_gdocs() + 
  theme(axis.title.x=element_blank())+
  scale_x_continuous(breaks=seq(1,12))
```

# Price trend
```{r}
price_month_year <- housing_data2 %>% group_by(month, year) %>% summarise(median=median(Prix.value.dzd)) %>% arrange(desc(median))
price_month_year
```

```{r}
 price_month_year$month<- match(price_month_year$month,month.abb)
```



```{r}
 ggplot(price_month_year) + 
  geom_line(aes(month,median,group=as.factor(year),color=as.factor(year))) + 
  theme_gdocs() + 
  scale_color_gdocs() + 
  theme(axis.title.x=element_blank())+
  scale_x_continuous(breaks=seq(1,12))
```







